---
title: "Tidying Data"
author: "Chris Terry"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: html_document
---

This is the updated version using new taxonomy and without Croat

The excel files used in this are not hosted on the github as part of the supplmentary information. The outputs are in the data folder. This is uploaded purely as a reference for the original data sources and methods used.


### Preliminaries

```{r, message=FALSE, warning=FALSE}
rm(list=ls())

try(setwd("C:/Users/pemb4504/Dropbox/Seed Predators/Redo"))
try(setwd("C:/Users/Chris/Dropbox/Seed Predators/Redo/"))

require('tidyverse')
require('ape')
require('phytools')
require('bipartite')
require('corrplot')
require('randomForestSRC')
require('ggRandomForests')
require('phylobase')
require('readxl')
require('knitr')
require('ggplot2')
require('dplyr')

source('plotweb function.R')


select<- dplyr::select

```

### Updated Data sources
```{r, message=FALSE, warning=FALSE}
Taxon19 <- read_excel("Data2019/Plant nomenclature_updated_20190114_final.xlsx")
InsectData <- read_excel("Data2019/Insect data_updated_cleaned for Chris.xlsx")
Sp_per_TaxonLevel <- read_excel('Data2019/AllBCIspecies.xlsx')

Trait<- read_csv('TraitData/Copy of SeedpredatorAndTraitdata.csv')

```


```{r}
InsectData%>%
  filter(IncludeInFoodWeb =='Yes')%>%
  select(InsectSpCode, FullSpeciesNameValid, Codigo, Order, Family, InsectGenus=Genus, TOTAL, KilledPerM2)-> FW
```

## Plant Susseceptibilty Data

For each plant, need: 

TotalunitsCollected, 

*Seed Predator Richness:*

SeedPreds_n
Bruchinae_n
Cerambycidae_n
Curculionidae_n
Lepidoptera_n
Coleoptera_n

*Seed Predator Presences:*
SeedPreds_pres
Bruchinae_pres
Cerambycidae_pres
Curculionidae_pres
Coleoptera_pres
Lepidoptera_pres 
Hymenoptera_pres


*Traits*
[see below]

```{r}

InsectData%>%
  select(FullSpeciesNameValid, Codigo, Order, Family, KilledPerM2)%>%
  group_by(Codigo)%>%
  count(Order)%>%
  spread(Order, n, fill = 0)%>%
  rename(Coleo_n = Coleoptera, Hymeno_n = Hymenoptera, Lepid_n = Lepidoptera)%>%
  mutate(Coleo_pres = (Coleo_n>0)*1, Hymeno_pres = (Hymeno_n>0)*1, Lepid_pres =(Lepid_n>0)*1)%>%
  mutate(SeedPred_n = sum(Coleo_n,Hymeno_n, Lepid_n ),
         SeedPred_pres =  (SeedPred_n>0)*1) -> OrderLevelPresence

```


# Non-BCI interaction frequency data

```{r}
left_join(InsectData,
          select(Trait, Codigo, TotUnits_collected),
          by='Codigo')%>%
  mutate( FracPredated = TOTAL/TotUnits_collected) -> InsectData

```

## Seed Predator Dissection Based Presence Data


```{r}
read_csv('Data2019/PredatedPerSpecies_dissections.csv') %>%
  rename(SeedPredationRate= Prop_predated ) ->DissectionData

Trait <- left_join(Trait, DissectionData, by='Codigo')

```

```{r}


Trait%>%
  count(Codigo)%>%
  arrange(desc(n))

Trait%>%
  count(Plant_species)%>%
  arrange(desc(n))

Trait%>%
  filter(!(Plant_species == 'Celtis_iguanaea' & Codigo=='CELS'))-> Trait # Remove the duplicate

Taxon19%>%
  select(Code4,Code6, Family, Plant_species19 = Plant_species) -> NamesToAddToTraits


Trait %>%
  select(-Family)%>%
  rename(Old_Plant_Species = Plant_species)%>%
  left_join(NamesToAddToTraits, by = c('Codigo' = 'Code4'))-> Trait


Trait%>%
  mutate(Tree_or_Liana = ifelse(Lifeform =='Tree', 'Tree', NA))%>%
    mutate(Tree_or_Liana = ifelse(Lifeform =='Liana', 'Liana', Tree_or_Liana))%>%
  select(-seed_fresh, -N_seedfull, -Seeds_collected, -Fruits_collected, - allstems, -min10stems, - seedvctlen1, - seedvctmean1, -densitycm3,
         -min20stems, -hemicellulose, -cellulose, -lignin , - VeinFT,
         -toughness, -specifictoughness, - Genus,-Species, - BCIspInFamily,-LamWS,
         -LamFT, -LamT, -LamD, -LMADISC_AVD, -RGR_50, -RGR_100)%>%
  separate(Plant_species19 , into = c('Genus19', 'Specific19', 'Var19'),
           extra = 'merge', fill = 'right', remove=FALSE)-> Trait
```

# Comparision of New Insect Data with Numbers in Trait DB

```{r}
OrderLevelPresence%>%
  arrange(desc(SeedPred_n))


Trait%>%
  select(Codigo,SeedPreds_n :Lepidoptera_pres )%>%
  rowwise()%>%
  mutate(Coleo_n = sum( Bruchinae_n,Cerambycidae_n,Curculionidae_n))%>%
  arrange(desc(SeedPreds_n))
  
```


### Replacing Trait DB with Predator numbers from NEw Insect Data

```{r}

Trait%>%
  select(- (SeedPreds_n  : Lepidoptera_pres))%>%
  left_join(OrderLevelPresence, by= 'Codigo') -> Trait
```


# Adding In Additional Traits

Variables reflecting resource availability at various spatial scales:
- fruitrecord (reflecting abundance of seeds in the BCI plant community)
- HEIGHT_AVG
- BCIspInFamily
- number of BCI species in genus #or similar; discussed above
- Number of reproductive individuals in the 50 ha plot 

Variables reflecting seed size and investment in seed defences:
- seed_dry
- EndocarpInvestment
- POLY_concentration

Variables reflecting temporal patterns and variation:
- cvseed
- Variable reflecting season of seed production #wet vs dry season species; data attached
- whether a species produces seeds at a time of the year when many other species produce seeds #awaiting Joe's response

Other
- Tree_or_liana
- RGR_10

```{r}
colnames(Trait)
```

Adding Additonal Traits from the various documents:

## Traits from BCI Plot Data

###number of BCI species in genus 

```{r}
Sp_per_TaxonLevel%>%
  separate(gs.Galdames, into = c('genus', 'specific'), extra='drop')%>%
  count(genus)%>%
  rename(SpInGenusOnBCI=n) -> SpeciesPerGenus

Sp_per_TaxonLevel%>%
  count(family)%>%
  rename(SpInFamilyOnBCI=n)-> SpeciesPerFamily

  Trait%>%
    left_join(SpeciesPerGenus, by=c('Genus19'='genus'))%>%
    left_join(SpeciesPerFamily, by=c('Family' = 'family'))-> Trait

```

Which ones are missing data?

## Species where 2019 genus name does not appear in big list of species
```{r}
sum(!(Trait$Genus19 %in%SpeciesPerGenus$genus))

Trait %>%
  filter( !(Genus19 %in%SpeciesPerGenus$genus))%>%
    select(Codigo, Old_Plant_Species, Plant_species19, Lifeform)%>% 
  kable
    
```

## Species where 2019 family does not appear in big BCI list 

```{r}
sum(!(Trait$Family %in%SpeciesPerFamily$family))

Trait %>%
  filter( !(Family%in%  SpeciesPerFamily$family))%>%
  arrange(Family)%>%
  select(Codigo, Old_Plant_Species, Plant_species19, Family, Lifeform)%>% 
  kable
```

###  HEIGHT_AVG 

```{r}
read_csv("TraitData/Max_height_and_RGR.csv")%>%
  select(SP, HEIGHT_AVG) -> height
  
  
  
  left_join(Trait,height, by=c('Code6'= 'SP'))-> Trait

```


### Number of reproductive individuals in the 50 ha plot

Method to select reproductive adults:

1. Calculate species-specific maximum DBH (DBHmax)

2.Select all individuals with DBH > 0.5 x DBHmax (Visser et al. 2016? Func. Ecol.)

3.For dioecious species, you might then divide by 2 to estimate number of seed-producing individuals (Bruinjen et al. 2016? Am. Nat.)

# For number in 50h plot
```{r}
BCIPlotdata <- read_delim("TraitData/BCIPlotdata.csv","\t", escape_double = FALSE, trim_ws = TRUE)
```

```{r}

BCIPlotdata %>%
  group_by(Latin) %>%
  summarise(MaxDBH = max(DBH)) %>% 
  left_join(BCIPlotdata, by='Latin') %>% 
  filter(DBH > 0.5*MaxDBH ) %>%
  group_by(Latin) %>%
  summarise(BCIReproductive = n_distinct(TreeID)) %>%
  separate(Latin,into=c('Genus', 'Specific')) %>%
  mutate(Plant_species = paste(Genus, Specific, sep='_')) %>%
  select(Plant_species,BCIReproductive) -> BCIReproductive

### Need to Try matching with both old name and new name
  Trait%>%
  left_join(BCIReproductive, by=c('Old_Plant_Species'='Plant_species'))%>%
  left_join(BCIReproductive, by=c('Plant_species19'='Plant_species'))%>%
  mutate(BCIReproductive = pmax(BCIReproductive.x,BCIReproductive.y,
                                na.rm=TRUE))%>%
  select(-BCIReproductive.x,-BCIReproductive.y)  -> Trait

```


##  EndocarpInvestment

```{r}
read_csv("TraitData/EndocarpInvestment.csv")%>%
  select(SP4, Endocarp_investment)-> EndocarpInvestment



Trait <- left_join(Trait, EndocarpInvestment,
                    by=c('Codigo'='SP4'))

```

## POLY_concentration

Use the total concentration of polyphenols (POLY_concentration) as an additional explanatory variable in the regression tree analyses, but ignore the other traits

```{r}
read_csv('TraitData/Polyphenoldata.csv')%>%
  select(Code, POLY_concentration) -> polyphenol


Trait <- left_join(Trait, polyphenol,
                    by=c('Codigo'='Code'))

```

## Variable reflecting season of seed production 

wet vs dry vs other season species;

 15 Jan through 30 March versus 1 June through 30 Nov)

```{r}
seed_predator_phenology <- read_csv("TraitData/seed_predator_phenology.csv")

hist(seed_predator_phenology$seed.vctmean1, breaks=52)
abline(v=c(15, 89, 152, 334), col='red')


seed_predator_phenology %>%
  select(sp, seed.vctmean1)%>%
  mutate(FruitSeason = 'Other')%>%
  mutate(FruitSeason = ifelse(seed.vctmean1>15 & seed.vctmean1 <89,
                              'Dry' ,  FruitSeason)) %>%
  mutate(FruitSeason = ifelse(seed.vctmean1>152 & seed.vctmean1 <334,
                              'Wet' ,  FruitSeason))%>%
  select(-seed.vctmean1) -> FruitSeason
  

Trait <- left_join(Trait, FruitSeason,
                    by=c('Codigo'='sp'))

```

## Co fruiting


Taking Data from the Supplementary Information of Wright et al Ecology, 97(10), 2016, pp. 2780–2790. 

From raw records of species being found in particular weeks across all traps, calculate which trees were co-fruiting with others. 

Method:
1. Collapse data into weekly list of fruiting trees.
2. Create list of speices codes to cycle through
3. For each Species, identify number of distint species that share a fruiting week with the species
4. Subtract 1, to report number of other species, not including the focal species
5. Any values of '-1' must therefore never appear in the fruit traps. They are set to NA

```{r}
Plants<-Trait$Codigo

read_csv('TraitData/CensusTrpSp.csv') %>%
  group_by(census) %>%
  distinct(sp) -> WeeklySp1

## Using other file in SI to translate from 6 number code to 4 number code
read_csv('WrightSIData2.csv') %>%
  select(code4, code6) %>%
  right_join(WeeklySp1,
             by=c('code6' = 'sp' )) %>%
  rename(Codigo = code4 )-> WeeklySp


mean(Plants %in% WeeklySp$Codigo) # 73% of specie sin Trait list found in Trait list

CoFruiters<- tibble(Codigo = Plants, 
                        CoFruit = NA)

for(i in 1:length(Plants)){
  
  FruitingWeeks<- filter(WeeklySp,
                         Codigo == CoFruiters$Codigo[i] )$census 
  filter(WeeklySp, 
         census %in% FruitingWeeks ) %>%
    summarise(n_distinct(Codigo) -1) %>%
    unlist() -> NumCoFru
  
  CoFruiters$CoFruit[i] <- NumCoFru
}


CoFruiters %>%
  mutate(CoFruit = ifelse(CoFruit==-1, NA, CoFruit)) -> CoFruiters
  

CoFruiters$CoFruit %>% hist


Trait <- left_join(Trait, CoFruiters, by='Codigo')
```

# Cleaning Columns and Saving
```{r}

Trait%>% 
  mutate(Coleo_n =  replace_na(Coleo_n,0),
                   Hymeno_n =  replace_na(Hymeno_n,0),
                   Lepid_n =  replace_na(Lepid_n,0),
                   Coleo_pres  =  replace_na(Coleo_pres , 0),
                   Hymeno_pres  =  replace_na(Hymeno_pres ,0),
                   Lepid_pres =  replace_na(Lepid_pres,0), 
                   SeedPred_n =  replace_na(SeedPred_n, 0),
                   SeedPred_pres =  replace_na(SeedPred_pres,0))-> Trait


write.csv(x= Trait, file = 'Data2019/TidyTrait.csv')
write.csv(x= FW, file = 'Data2019/FW.csv')
```


# Phylogeny

```{r}
## See Phylgeny Checking Document for breakdown of species
```

## Species that were in the phylogeny  under their old name, but not their new:
```{r}
load('Data2019/SpellCorrectedPhylo')

InPhylo1 <- Taxon19$Plant_species %in% Phylo1$tip.label
sum(InPhylo1)

PhyloPresent <-  Phylo1$tip.label%in% Taxon19$Plant_species
PhylOldGood<- Phylo1$tip.label%in%Taxon19$OldSpecies

ToReplace<-Phylo1$tip.label[!PhyloPresent &PhylOldGood]

TipLabels<- Phylo1$tip.label

for(i in 1:length(ToReplace)){
  WhereInTaxon19 <-  which(Taxon19$OldSpecies == ToReplace[i])
  WhereInPhylogeny<- which(TipLabels          == ToReplace[i])
  TipLabels[WhereInPhylogeny]<- Taxon19$Plant_species[WhereInTaxon19]
}

Phylo1$tip.label <- TipLabels

InPhylo1 <- Taxon19$Plant_species %in% Phylo1$tip.label
sum(InPhylo1)

```

## Adding to species to phylogeny where genus is already there

```{r}

Phylo1Genuses <- unique(str_split_fixed(Phylo1$tip.label, pattern = '_',n =  6)[,1])
ToAddToPhylo<-Taxon19[!InPhylo1 & (Taxon19$Genus%in% Phylo1Genuses),] # 84 to add
kable(ToAddToPhylo$Plant_species)

PhyloExtraSpec<-Phylo1
PhyloExtraSpec$edge.length<- PhyloExtraSpec$edge.length + 0.001 # NB smallest naturally in web =  0.018142    

PhyloExtraSpec <-force.ultrametric(PhyloExtraSpec)

## Adding a small distance to all edge lengths that are zero to randomly resolve polytomies..,

for(i in 1: nrow(ToAddToPhylo)){
  PhyloExtraSpec <- add.species.to.genus(tree = PhyloExtraSpec,
                                       species =ToAddToPhylo$Plant_species[i],
                                       genus = ToAddToPhylo$Genus[i],
                                       where = 'root')
  }

InPhyloExtraSpec <- Taxon19$Plant_species %in% PhyloExtraSpec$tip.label
sum(InPhyloExtraSpec)


write.tree(PhyloExtraSpec, file = 'Data2019/PhyloExtraSpec.tree')

Trait$InPhylogeny <- Trait$Plant_species19 %in% PhyloExtraSpec$tip.label

colnames(Trait)

```
Only 57 compltely unaccounted for...

```{r}
sum(!InPhyloExtraSpec)


```
### Adding phylogeny to table and reordering
```{r}
ReorderedTrait <- select_(Trait, 

"Codigo"              ,"Code6"               ,
"Old_Plant_Species"  ,"Family"             ,
"Plant_species19"     ,"Genus19"            ,
"Specific19"          ,"Var19"  ,"InPhylogeny" ,
"TotUnits_collected"  ,"Lifeform"           ,
"Freestanding"        ,"Woody_or_nonwoody"  ,
"seed_dry"            ,"fruitrecord"        ,
"cvseed"              ,
"RGR_10"             ,"SpInGenusOnBCI"     ,
"SpInFamilyOnBCI"     ,"HEIGHT_AVG"         ,
"BCIReproductive"     ,"Endocarp_investment",
"POLY_concentration"  ,"FruitSeason"        ,
"CoFruit"              ,"Tot_dissected"      ,
"Tot_predated"        ,"SeedPredationRate"  ,
"Tree_or_Liana"       ,"Coleo_n"            ,
"Hymeno_n"            ,"Lepid_n"            ,
"Coleo_pres"          ,"Hymeno_pres"        ,
"Lepid_pres"          ,"SeedPred_n"         ,
"SeedPred_pres"       
)
write.csv(x= ReorderedTrait, file = 'Data2019/TidyTraitReOrderWithPhylo.csv')

```

