---
title: "Phylogenetic Signal Analyses"
author: "J C D Terry & S Gripenberg"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: 
  html_document: 
    toc: yes
---

# Packages and Data

```{r, message=FALSE, warning=FALSE}
rm(list=ls())

require(tidyverse)
require(knitr)
require(phytools)
require(ape)
require(phytools)
require(caper)
require(picante)

select<- dplyr::select # to ensure dplyr version of select is default
```

### Versions used (see also session Info in html outputs):

 picante_1.8     nlme_3.1-140    vegan_2.5-5     lattice_0.20-38
 permute_0.9-5   caper_1.0.1     mvtnorm_1.0-11  MASS_7.3-51.4  
 phytools_0.6-99 maps_3.3.0      ape_5.3         knitr_1.23     
 forcats_0.4.0   stringr_1.4.0   dplyr_0.8.1     purrr_0.3.2    
 readr_1.3.1     tidyr_0.8.3     tibble_2.1.3    ggplot2_3.2.0  
 tidyverse_1.2.1


```{r}
FW<-read_csv('../Data/FW.csv')
Trait<- read_csv('../Data/TidyTrait.csv')
PhyloExtraSpec<-read.tree('../Data/PhyloExtraSpec.tree')

```

# Data Manipulation

Takes species that are in phylogeny, joins trait data to create a data frame, selects only a few of the columns, replaces any spaces in the plant names with underscores, creates new columns that include logical tests of whether the plants ins 'well sampled' or 'predated'. 


```{r message=FALSE, warning=FALSE}

data.frame(Phylo_sp=PhyloExtraSpec$tip.label)%>%
  left_join(Trait, by= c('Phylo_sp' = 'Plant_species19')) %>%
  select(taxa=Phylo_sp,Family,TotUnits_collected, SeedPred_pres,
         Hymeno_pres, Lepid_pres , Coleo_pres)-> PhyloDF
```

## Do Seed Predators of Different Orders Partition or Aggregate on Particular Plants

Chi-Squared Tests to test if co-attack is greater than expected

```{r message=FALSE, warning=FALSE}
PhyloDF%>%
  filter(TotUnits_collected>200) %>%
  select(Hymeno_pres ,Lepid_pres, Coleo_pres)%>%
  mutate(HandC = Hymeno_pres&Coleo_pres,
         HandL = Hymeno_pres&Lepid_pres,
         CandL = Coleo_pres&Lepid_pres,
         HandCandL =  Hymeno_pres&Coleo_pres&Lepid_pres)-> ChiSqDat

ChiSqDat%>%
  summarise_all(sum)

chisq.test(x=ChiSqDat$Hymeno_pres, y=ChiSqDat$Lepid_pres)
chisq.test(x=ChiSqDat$Hymeno_pres, y=ChiSqDat$Coleo_pres)
chisq.test(x=ChiSqDat$Coleo_pres, y=ChiSqDat$Lepid_pres)

```


# Phylogenetic Signal
## Getting Data into Format
```{r}
## Using comparative.data() funbction to match seed data with phylogeny
PhyloDF$Hymeno_pres<- as.character(PhyloDF$Hymeno_pres)
PhyloDF$Lepid_pres <- as.character(PhyloDF$Lepid_pres)
PhyloDF$Coleo_pres <- as.character(PhyloDF$Coleo_pres )

 PhyloDF %>% 
   select(taxa,Coleo_pres:SeedPred_pres ) -> DF2 
 
SimplePlotPhylo<- PhyloExtraSpec
#SimplePlotPhylo$tip.label <- levels( SimplePlotPhylo$tip.label) # remove the factoring
WellSampledTree <- drop.tip(SimplePlotPhylo, tip = PhyloDF$taxa[PhyloDF$TotUnits_collected <200])
WellSampledTree$node.label <- 1:length(WellSampledTree$node.label)
WellSampledTree$edge.length  <-WellSampledTree$edge.length +0.001

WellSampledTreeCaper <- comparative.data(phy = WellSampledTree, data = DF2, names.col = taxa )
```

## Signal In Presence of Different Orders

```{r fig.height=3, fig.width=3}

PHYLD<-phylo.d(data = WellSampledTreeCaper, binvar=SeedPred_pres)
PHYLD
plot(PHYLD)

PHYLDWasp<-phylo.d(data = WellSampledTreeCaper, binvar=Hymeno_pres)
PHYLDMoth<-phylo.d(data = WellSampledTreeCaper, binvar=Lepid_pres)
PHYLDBeetle<-phylo.d(data = WellSampledTreeCaper, binvar=Coleo_pres)

PHYLDWasp
plot(PHYLDWasp)
PHYLDMoth
plot(PHYLDMoth)
PHYLDBeetle
plot(PHYLDBeetle)
```

## Signal in Continuous responses (Seed Predator Load and Rate)

```{r}
  BkTestPhylo <- PhyloExtraSpec

Trait%>%
  select(Plant_species19,SeedPred_n, SeedPredationRate,TotUnits_collected) %>%
  filter(TotUnits_collected>200,
         Plant_species19 %in% BkTestPhylo$tip.label)%>%
  mutate(SeedPred_n = ifelse(is.na(SeedPred_n),0,SeedPred_n),
         SeedPredationRate = ifelse(is.na(SeedPredationRate), 0, SeedPredationRate))%>%
  as.data.frame()->BkTestTraits

# Drop from phylogeny those not well sampled in trait database
TO_DROP <- BkTestPhylo$tip.label[!(BkTestPhylo$tip.label %in% BkTestTraits$Plant_species19)]
WSTree<- drop.tip(BkTestPhylo,   tip =TO_DROP)

# remove polytomies
WSTree <- multi2di(WSTree, random = TRUE)

# Make sure edge length isn't zero
WSTree$edge.length <- WSTree$edge.length+0.001 

# Put them in the right order:
BkTestTraits <- BkTestTraits[   match(WSTree$tip.label, BkTestTraits$Plant_species19),   ] 

```

### Phylogenetic Signal of Predator Diversity
```{r}
set.seed(1)
phylosignal(BkTestTraits$SeedPred_n,WSTree)
phytools::phylosig(WSTree,BkTestTraits$SeedPred_n, test=TRUE, nsim = 50000) # Check using other package

```

### Phylogenetic Signal of Predation Rate

```{r}
set.seed(1)
phylosignal(BkTestTraits$SeedPredationRate,WSTree)
phytools::phylosig(WSTree,BkTestTraits$SeedPredationRate, test=TRUE, nsim = 50000) # Check using other package
```

# Session Info

```{r}
sessionInfo()

```


