---
title: "Random Forest Analyses"
author: "J C D  Terry & S Gripenberg"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: 
  html_document: 
    number_sections: yes
    toc: yes
---

Code used to conduct random analyses for Gripenberg et al. 'Patterns of host use by insect seed predators in a species-rich tropical forest'.

# Packages and Data

```{r, message=FALSE, warning=FALSE}

require(tidyverse)
require(bipartite)
require(corrplot)
require(randomForest)
require(randomForestSRC)
require(ggRandomForests)

require(knitr)
require(broom)
require(RColorBrewer)
require(caret)
require(cowplot)
require(pdp)
require(gridExtra)


### Additional Packages required
# install.packages("party") # don't load as overwrites other packages
# install.packages('e1071') #  needed for party package

select<- dplyr::select # to ensure dplyr version of select is default

```

```{r}
FW<-read_csv('../Data/FW.csv')
Trait<- read_csv('../Data/TidyTrait.csv')

```

### Basic Data Wrangling:
```{r}

Trait %>%
  filter(Woody_or_nonwoody == 'Woody') -> WoodyTraits

WoodyTraits %>%
  filter(TotUnits_collected>200) -> WellSampledWoody

```

# Justification for selecting just those with over 200 sampled:
```{r message=FALSE}
WoodyTraits %>%
  ggplot(aes(x= TotUnits_collected,fill=factor(SeedPred_pres)))+
  geom_histogram(position = "stack", col='black')+
  scale_x_log10(breaks=c(1,10, 100, 1000, 10000)) +
  annotation_logticks(sides = 'b', short = unit(0.1, "cm"), mid = unit(0.1, "cm")) +
  geom_vline(aes(xintercept = 200), col= 'grey', linetype =2)+
  labs(x='Seed Sample Size', y='Number of species')+
  scale_fill_manual(values = c('white', 'black'),
                    name='Predator\nPresence\nObserved',
                    labels=c('No', 'Yes'))+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"))

ggsave('../Figures/FigureS1.png', width = 5, height=5, dpi = 500)
ggsave('../Figures/FigureS1.pdf', width = 5, height=5)


WoodyTraits %>%
  glm(factor(SeedPred_pres) ~TotUnits_collected,
      data = .,
      family = binomial(link='logit')) %>%
  summary



WoodyTraits %>%
  filter(TotUnits_collected>200) %>%
  glm(factor(SeedPred_pres) ~TotUnits_collected,
      data = .,
      family = binomial(link='logit')) %>%
  summary

```


```{r}


WoodyTraits %>%
  glm(factor(SeedPred_pres) ~TotUnits_collected,
      data = .,
      family = binomial(link='logit')) -> fit11

predict(fit11, data.frame(TotUnits_collected = 10000), type= 'response')

boot::inv.logit( -0.7396426 + 0.0013662*10000) # to double check

WoodyTraits %>%
  mutate(log10Collected = log10(TotUnits_collected))%>%
  glm(factor(SeedPred_pres) ~log10Collected,
      data = .,
      family = binomial(link='logit')) -> fit22

predict(fit22, data.frame(log10Collected = 4), type= 'response')


```

# Prediction of Seed Predation from Traits

## Data Assessment

### How many positive's are being discarded by cutting at 200?

Discarding those with less than 200 samples throws away 70% of the observations of seed predators. However it does double the fraction of found seed predators. 

```{r}
WoodyTraits$SeedPred_pres %>% sum
WoodyTraits$SeedPred_pres %>% mean

WellSampledWoody$SeedPred_pres %>% sum
WellSampledWoody$SeedPred_pres %>% mean

```

### Correlation between traits
```{r}
Trait %>%
  select(fruitrecord, HEIGHT_AVG , SpInFamilyOnBCI, SpInGenusOnBCI, BCIReproductive, 
         seed_dry, Endocarp_investment, POLY_concentration, 
         cvseed,CoFruit, RGR_10, TotUnits_collected)%>%
  rename(`Units Collected`=TotUnits_collected,
         `Tree Height`=HEIGHT_AVG,
         `Seed mass`=seed_dry,
         `Local seed\ncrop size`=fruitrecord,
         `Interannual\ncrop size variation`=cvseed,
         `Overlap in\nfruit production`=CoFruit,
         `Local tree\nabundance`=BCIReproductive,
         `Polyphenol\nconcentration`=POLY_concentration,
         `Relative Growth Rate`=RGR_10,
         `BCI family-level\ndiversity`=SpInFamilyOnBCI,
         `BCI genus-level\ndiversity`=SpInGenusOnBCI,
         `Endocarp investment`=Endocarp_investment)%>%
  cor(method='spearman', use='pair') -> CORR

corrplot(CORR, type = 'lower', method='color',tl.col = 1,tl.cex = 0.8,
         diag = FALSE,addCoef.col = "black", addCoefasPercent = TRUE, order = 'original')



png('../Figures/TraitCorrelation.png', 6, 6, 'in', res = 300)
corrplot(CORR, type = 'lower', method='color',tl.col = 1,tl.cex = 0.8,
         diag = FALSE,addCoef.col = "black", addCoefasPercent = TRUE, order = 'original')
dev.off()



```

### Further Data Cleaning


```{r}
WellSampledWoody$FruitSeason<- factor(WellSampledWoody$FruitSeason)
WellSampledWoody$SeedPred_pres <- factor(WellSampledWoody$SeedPred_pres, 
                                         levels = c(1,0), labels = c('Predated','Not-Predated'))

WellSampledWoody <- as.data.frame(WellSampledWoody)
WellSampledWoody$Freestanding<- factor(WellSampledWoody$Freestanding)
WellSampledWoody$Lifeform<- factor(WellSampledWoody$Lifeform)


```

### Removing tiny seeds from quantitative responses

Figs and other species groups with tiny seeds don't allow a straightforward count of how many seeds have been attacked. 

```{r}
MinSeedSize<- 0.001

WellSampledWoody%>%
  filter(seed_dry > MinSeedSize) -> WellSampledWoody_bigseeds

```


### Fraction Missing Data
```{r}
Trait %>%
  select(fruitrecord, HEIGHT_AVG , SpInFamilyOnBCI, SpInGenusOnBCI, BCIReproductive, 
         seed_dry, Endocarp_investment, POLY_concentration, Freestanding,
         cvseed,CoFruit, RGR_10, TotUnits_collected)%>%
  purrr::map_dbl(~ mean(is.na(.))) -> AllDataMissing

WellSampledWoody  %>% 
  select(fruitrecord, HEIGHT_AVG , SpInFamilyOnBCI, SpInGenusOnBCI, BCIReproductive, 
         seed_dry, Endocarp_investment, POLY_concentration, Freestanding,
         cvseed,CoFruit, RGR_10, TotUnits_collected)%>%
  purrr::map_dbl(~ mean(is.na(.))) -> WellSampledMissing


data.frame(WellSampledMissing,AllDataMissing)%>%
  magrittr::multiply_by(100)%>%
  magrittr::set_colnames(c('Well-Sampled Missing %', 'All Data Missing %'))%>%
  rownames_to_column('Trait')%>%
  arrange(WellSampledMissing)%>%
  knitr::kable(digits = 1)

```

## Spine plots of traits against seed predator presence

### Main Text Plots

```{r}
D <- WellSampledWoody

png('../Figures/ExampleSpinePlots.png',height= 5, width = 8, res= 600, units='in')
par(mfrow=c(1,2), xpd=TRUE)

plot(SeedPred_pres~ HEIGHT_AVG,   data=D, xlab='Tree Height (m)', ylab='', col=c('tomato3','white'))
mtext('a)',side = 3, at = -0.1, padj = -1)
plot(SeedPred_pres~ log10(seed_dry), data=D, xlab=expression(Seed~mass~(log[10]~g)),
     ylab='', col=c('tomato3','white'))
mtext('b)',side = 3, at = -0.1, padj = -1)
dev.off()

```


### Supplementary Plots
```{r}



png('../Figures/SpinePlotsa.png',height= 12, width = 8, res= 600, units='in')
par(mfrow=c(4,2))

plot(SeedPred_pres~ log10(TotUnits_collected),   data=D, xlab='Units Collected (Log 10)', ylab='')
plot(SeedPred_pres~ HEIGHT_AVG,   data=D, xlab='Tree Height', ylab='')
plot(SeedPred_pres~ log10(seed_dry),   data=D, xlab='Seed mass (Log10)', ylab='')
plot(SeedPred_pres~ log10(fruitrecord),   data=D, xlab='Local seed\ncrop size', ylab='')
plot(SeedPred_pres~ cvseed,   data=D, xlab='Interannual\ncrop size variation', ylab='')
plot(SeedPred_pres~ CoFruit,   data=D, xlab='Overlap in\nfruit production', ylab='')
plot(SeedPred_pres~ log10(BCIReproductive),   data=D, xlab='Local tree\nabundance (Log 10)', ylab='')
dev.off()
png('../Figures/SpinePlotsb.png',height= 12, width = 8, res= 600, units='in')
par(mfrow=c(4,2))
plot(SeedPred_pres~ POLY_concentration,   data=D, xlab='Polyphenol\nconcentration', ylab='')
plot(SeedPred_pres~ RGR_10,   data=D, xlab='Relative Growth Rate', ylab='')
plot(SeedPred_pres~ SpInFamilyOnBCI,   data=D, xlab='BCI family-level\ndiversity', ylab='')
plot(SeedPred_pres~ SpInGenusOnBCI,   data=D, xlab='BCI genus-level\ndiversity', ylab='')
plot(SeedPred_pres~ Endocarp_investment,   data=D, xlab='Endocarp investment', ylab='')
plot(SeedPred_pres~ FruitSeason,   data=D, xlab='Fruiting season', ylab='')
plot(SeedPred_pres~ Freestanding,   data=D, xlab='Freestanding', ylab='')
dev.off()


pdf('../Figures/SpinePlotsa.pdf',height= 12, width = 8)
par(mfrow=c(4,2))

plot(SeedPred_pres~ log10(TotUnits_collected),   data=D, xlab='Units Collected (Log 10)', ylab='')
plot(SeedPred_pres~ HEIGHT_AVG,   data=D, xlab='Tree Height', ylab='')
plot(SeedPred_pres~ log10(seed_dry),   data=D, xlab='Seed mass (Log10)', ylab='')
plot(SeedPred_pres~ log10(fruitrecord),   data=D, xlab='Local seed\ncrop size', ylab='')
plot(SeedPred_pres~ cvseed,   data=D, xlab='Interannual\ncrop size variation', ylab='')
plot(SeedPred_pres~ CoFruit,   data=D, xlab='Overlap in\nfruit production', ylab='')
plot(SeedPred_pres~ log10(BCIReproductive),   data=D, xlab='Local tree\nabundance (Log 10)', ylab='')
dev.off()
pdf('../Figures/SpinePlotsb.pdf',height= 12, width = 8)
par(mfrow=c(4,2))
plot(SeedPred_pres~ POLY_concentration,   data=D, xlab='Polyphenol\nconcentration', ylab='')
plot(SeedPred_pres~ RGR_10,   data=D, xlab='Relative Growth Rate', ylab='')
plot(SeedPred_pres~ SpInFamilyOnBCI,   data=D, xlab='BCI family-level\ndiversity', ylab='')
plot(SeedPred_pres~ SpInGenusOnBCI,   data=D, xlab='BCI genus-level\ndiversity', ylab='')
plot(SeedPred_pres~ Endocarp_investment,   data=D, xlab='Endocarp investment', ylab='')
plot(SeedPred_pres~ FruitSeason,   data=D, xlab='Fruiting season', ylab='')
plot(SeedPred_pres~ Freestanding,   data=D, xlab='Freestanding', ylab='')
dev.off()
```

# Fitting Random Forests to well-sampled species

```{r}
CTRL <- party::cforest_control(mtry=5,
                               ntree=5000, 
                               mincriterion = 0)
```

## Seed Predator Presence

```{r}

set.seed(1)

party::cforest(SeedPred_pres ~ fruitrecord + SpInFamilyOnBCI + SpInGenusOnBCI+
                 BCIReproductive + Freestanding + HEIGHT_AVG+
                 seed_dry + Endocarp_investment + POLY_concentration +
                 cvseed+ FruitSeason  +CoFruit+RGR_10,
               data=as.data.frame(WellSampledWoody), controls = CTRL) -> RF_Wood_WS_CF

oobPredicted=predict(RF_Wood_WS_CF,OOB=TRUE)
accuracy<-table( as.data.frame(WellSampledWoody)$SeedPred_pres,oobPredicted)

## Confusion Matrix
accuracy
(accuracy / sum(accuracy))*100

caret::cforestStats(RF_Wood_WS_CF)

caret::confusionMatrix( as.data.frame(WellSampledWoody)$SeedPred_pres,oobPredicted)

X1<-party::varimp(RF_Wood_WS_CF)
```


### Testing other values of mtry:

```{r}
MTryTable <-data.frame(Mtry = 1:13, Acc = NA, Kappa = NA)

for (i in 1:13){
  set.seed(1)
  CTRL <- party::cforest_control(ntree=5000, mtry = i)
  
  party::cforest(SeedPred_pres ~ fruitrecord + SpInFamilyOnBCI + SpInGenusOnBCI+
                   BCIReproductive + Freestanding + HEIGHT_AVG+
                   seed_dry + Endocarp_investment + POLY_concentration +
                   cvseed+ FruitSeason  +CoFruit+RGR_10,
                 data=as.data.frame(WellSampledWoody), controls = CTRL) -> RF_Wood_WS_CFvvv
  
  xxx<-caret::cforestStats(RF_Wood_WS_CFvvv)
  MTryTable$Acc[i] <- xxx[1]
  MTryTable$Kappa[i] <- xxx[2]
}
MTryTable %>% knitr::kable(digits = 4)
```



## Predator Diversity

Seed predator species load

```{r}
set.seed(1)
# 
party::cforest(SeedPred_n ~ fruitrecord+ HEIGHT_AVG + SpInFamilyOnBCI + SpInGenusOnBCI+
                 BCIReproductive + Freestanding +
                 seed_dry + Endocarp_investment + POLY_concentration +
                 cvseed+ FruitSeason  +CoFruit+RGR_10,
               data=as.data.frame(WellSampledWoody), controls = CTRL) -> RF_Wood_WS_CF_2

RF_Wood_WS_CF_2

caret::cforestStats(RF_Wood_WS_CF_2)
X2<-party::varimp(RF_Wood_WS_CF_2)
```

## Seed Predation Rate (Dissection)

seed predator abundance / total count

```{r}
set.seed(1)

WellSampledWoody_bigseeds%>%
  filter(!is.na(SeedPredationRate)) %>%
  as.data.frame -> For_4 # two NAs for some reason??


party::cforest(SeedPredationRate ~ fruitrecord+ HEIGHT_AVG + SpInFamilyOnBCI +
                 SpInGenusOnBCI+ BCIReproductive + Freestanding +
                 seed_dry + Endocarp_investment + POLY_concentration + 
                 cvseed+ FruitSeason  +CoFruit+RGR_10, 
               data=For_4, controls = CTRL) -> RF_Wood_WS_CF_4

RF_Wood_WS_CF_4
caret::cforestStats(RF_Wood_WS_CF_4)

X4<-party::varimp(RF_Wood_WS_CF_4)
```

## Variable Importance Plots

```{r warning=FALSE}
data.frame('Importance' = X1,
           'Variable'=names(X1),
           'Response' = 'a.~Incidence:~kappa==0.049') ->a
data.frame('Importance' = X2,
           'Variable'=names(X2),
           'Response' = 'b.~Richness:~R^{2}==0.10')->b
data.frame('Importance' = X4,
           'Variable'=names(X4),
           'Response' = 'c.~Rate:~R^{2}==0.057') ->d

Order<-as.character(arrange(a, Importance)$Variable)

bind_rows(a,b,d)%>%
  rownames_to_column()%>%
  mutate(Importance =ifelse(Importance<0, 0, Importance))%>%
  mutate(Variable = factor(Variable, levels = Order))%>%
  ggplot(aes(y=Importance ,x=Variable))+
  geom_bar(stat='identity')+
  scale_x_discrete(limits = c( 'Freestanding',
                               'Endocarp_investment',
                               'fruitrecord',
                               'RGR_10',
                               'SpInGenusOnBCI',
                               'BCIReproductive', 
                               'cvseed',  
                               'POLY_concentration',
                               'SpInFamilyOnBCI',
                               'FruitSeason',
                               'CoFruit', 
                               'seed_dry',
                               'HEIGHT_AVG'),   
                   
                   labels=c(   'Freestanding',
                               'Endocarp investment',
                               'Local seed\ncrop size',
                               'Relative growth rate',
                               'BCI genus-level\ndiversity',
                               'Local tree\nabundance',
                               'Interannual\ncrop size variation',
                               'Polyphenol\nconcentration', 
                               'BCI family-level\ndiversity',
                               'Fruiting season',
                               'Overlap in\nfruit production', 
                               'Seed mass',
                               'Tree height'))+
  facet_grid(.~Response, scales = 'free', labeller = "label_parsed") +
  coord_flip()+
  ylab('Relative Importance of Variable')+
  xlab('')+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        strip.background =element_rect(fill="white"))

ggsave('../Figures/VarImpPlot.png', width=12, height=10, dpi=500)
ggsave('../Figures/VarImpPlot.pdf', width=12, height=10)

```

## Partial Dependence Plots

Because these take a long time to run, they have been pre-calculated for this knitr.
```{r eval=FALSE}
PartialPlotA1 <- partial(object = RF_Wood_WS_CF  ,train=as.data.frame(WellSampledWoody),progress='text',pred.var = 'HEIGHT_AVG')
PartialPlotA2 <- partial(object = RF_Wood_WS_CF  ,train=as.data.frame(WellSampledWoody),progress='text',pred.var = 'seed_dry')
PartialPlotB1 <- partial(object = RF_Wood_WS_CF_2,train=as.data.frame(WellSampledWoody),progress='text',pred.var = 'HEIGHT_AVG')
PartialPlotB2 <- partial(object = RF_Wood_WS_CF_2,train=as.data.frame(WellSampledWoody),progress='text',pred.var = 'seed_dry')
PartialPlotD1 <- partial(object = RF_Wood_WS_CF_4,train=For_4,progress='text',pred.var = 'HEIGHT_AVG')
PartialPlotD2 <- partial(object = RF_Wood_WS_CF_4,train=For_4,progress='text',pred.var = 'seed_dry')

save(PartialPlotA1,file = '../PPOutputs/PPA1')
save(PartialPlotA2,file = '../PPOutputs/PPA2')
save(PartialPlotB1,file = '../PPOutputs/PPB1')
save(PartialPlotB2,file = '../PPOutputs/PPB2')
save(PartialPlotD1,file = '../PPOutputs/PPD1')
save(PartialPlotD2,file = '../PPOutputs/PPD2')
```

```{r message=FALSE, warning=FALSE}
load('../PPOutputs/PPA1')
load('../PPOutputs/PPA2')
load('../PPOutputs/PPB1')
load('../PPOutputs/PPB2')
load('../PPOutputs/PPD1')
load('../PPOutputs/PPD2')

### Log some 
plottedA1<-ggplot(PartialPlotA1, aes(HEIGHT_AVG,yhat))+geom_step() +
  xlab('Tree height') + ylab(expression(paste("        Partial\nDependence (", hat(y),')')))
plottedA2<-ggplot(PartialPlotA2, aes(seed_dry,yhat))+
  geom_step()+scale_x_log10() + xlab('Seed mass')+ ylab('')

plottedB1<-ggplot(PartialPlotB1,aes(HEIGHT_AVG,yhat))+geom_step() +
  xlab('Tree height') + ylab(expression(paste("        Partial\nDependence (", hat(y),')')))
plottedB2<-ggplot(PartialPlotB2, aes(seed_dry,yhat))+
  geom_step()+scale_x_log10() + xlab('Seed mass')+ ylab('')

plottedD1<-ggplot(PartialPlotD1, aes(HEIGHT_AVG,yhat))+geom_step() +
  xlab('Tree height') + ylab(expression(paste("        Partial\nDependence (", hat(y),')')))
plottedD2<-ggplot(PartialPlotD2,aes(seed_dry,yhat))+
  geom_step()+scale_x_log10() + xlab('Seed mass')+ ylab('')

AllPDP <-plot_grid(plottedA1,
                   plottedA2,
                   plottedB1,
                   plottedB2,
                   plottedD1,
                   plottedD2,  ncol=2, 
                   labels = c('a) Seed Predator Incidence', '', 
                              'b) Seed Predator Richness', '', 
                              'c) Seed Predation Rate', ''),
                   hjust = -0.2, vjust = 1.2,
                   scale=0.9)
AllPDP
ggsave('../Figures/PartialDependencePlots.png',AllPDP,width = 12, height=12, dpi=600)
ggsave('../Figures/PartialDependencePlots.pdf',AllPDP,width = 12, height=12)

```

# Fitting Random Forests to all plant species, including sample size as a co-predictor

## Seed Predator Presence

```{r}
WoodyTraits$FruitSeason<- factor(WoodyTraits$FruitSeason)
WoodyTraits$SeedPred_pres <- as.factor(WoodyTraits$SeedPred_pres )
WoodyTraits$Freestanding <- as.factor(WoodyTraits$Freestanding )
WoodyTraits<- as.data.frame(WoodyTraits)

set.seed(1)

party::cforest(SeedPred_pres ~ TotUnits_collected + fruitrecord+ HEIGHT_AVG + SpInFamilyOnBCI + SpInGenusOnBCI+
                 BCIReproductive +  Freestanding +
                 seed_dry + Endocarp_investment + POLY_concentration + 
                 cvseed+ FruitSeason  +CoFruit+RGR_10, 
               data=WoodyTraits, controls = CTRL) -> RF_Wood_all_CF


party::cforest(SeedPred_pres ~ TotUnits_collected + fruitrecord+ HEIGHT_AVG + SpInFamilyOnBCI + SpInGenusOnBCI+
                 BCIReproductive +  Freestanding +
                 seed_dry + Endocarp_investment + POLY_concentration + 
                 cvseed+ FruitSeason  +CoFruit+RGR_10, 
               data=WoodyTraits, controls = CTRL) -> RF_Wood_all_CF


oobPredicted=predict(RF_Wood_all_CF,OOB=TRUE)
accuracy<-table( WoodyTraits$SeedPred_pres,oobPredicted)

## Confusion Matrix
accuracy
(accuracy / sum(accuracy))*100

caret::cforestStats(RF_Wood_all_CF)

X1all<-party::varimp(RF_Wood_all_CF)

```

## Predator Diversity

Seed predator species load

```{r}
set.seed(1)

party::cforest(SeedPred_n ~ TotUnits_collected + fruitrecord+ HEIGHT_AVG + SpInFamilyOnBCI + SpInGenusOnBCI+
                 BCIReproductive + Freestanding + 
                 seed_dry + Endocarp_investment + POLY_concentration + 
                 cvseed+ FruitSeason  +CoFruit+RGR_10, 
               data=WoodyTraits, controls = CTRL) -> RF_Wood_all_CF_2

RF_Wood_all_CF_2

caret::cforestStats(RF_Wood_all_CF_2)
X2all<-party::varimp(RF_Wood_all_CF_2)
```

## Seed Predation Rate (Dissection)

seed predator abundance / total count

```{r}
set.seed(1)

WoodyTraits%>%
  filter(seed_dry > MinSeedSize)%>%
  filter(!is.na(SeedPredationRate)) %>%
  as.data.frame -> For_4 # 


party::cforest(SeedPredationRate ~ TotUnits_collected + fruitrecord+ HEIGHT_AVG + SpInFamilyOnBCI +
                 SpInGenusOnBCI+ BCIReproductive +  Freestanding +
                 seed_dry + Endocarp_investment + POLY_concentration + 
                 cvseed+ FruitSeason  +CoFruit+RGR_10, 
               data=For_4, controls = CTRL) -> RF_Wood_all_CF_4

RF_Wood_all_CF_4
caret::cforestStats(RF_Wood_all_CF_4)

X4all<-party::varimp(RF_Wood_all_CF_4)
```

## Variable importance including poorly sampled data

```{r}
data.frame('Importance' = X1all,
           'Variable'=names(X1all),
           'Response' = 'a.~Incidence') ->a_all
data.frame('Importance' = X2all,
           'Variable'=names(X2all),
           'Response' = 'b.~Richness')->b_all
data.frame('Importance' = X4all,
           'Variable'=names(X4all),
           'Response' = 'c.~Rate') ->d_all

Order<-as.character(arrange(a_all, Importance)$Variable)

bind_rows(a_all,b_all,d_all)%>%
  rownames_to_column()%>%
  mutate(Importance =ifelse(Importance<0, 0, Importance))%>%
  mutate(Variable = factor(Variable, levels = Order))%>%
  ggplot(aes(y=Importance ,x=Variable))+
  geom_bar(stat='identity')+
  scale_x_discrete(limits = c( 'Freestanding',
                               'Endocarp_investment',
                               'fruitrecord',
                               'RGR_10',
                               'SpInGenusOnBCI',
                               'BCIReproductive', 
                               'cvseed',  
                               'POLY_concentration',
                               'SpInFamilyOnBCI',
                               'FruitSeason',
                               'CoFruit', 
                               'seed_dry',
                               'HEIGHT_AVG',
                               'TotUnits_collected'),   
                   
                   labels=c(
                     'Freestanding',
                               'Endocarp investment',
                               'Local seed\ncrop size',
                               'Relative growth rate',
                               'BCI genus-level\ndiversity',
                               'Local tree\nabundance',
                               'Interannual\ncrop size variation',
                               'Polyphenol\nconcentration', 
                               'BCI family-level\ndiversity',
                               'Fruiting season',
                               'Overlap in\nfruit production', 
                               'Seed mass',
                               'Tree height',
                     'Total Units Collected'))+
  facet_grid(.~Response, scales = 'free', labeller = "label_parsed") +
  coord_flip()+
  ylab('Relative Importance of Variable')+
  xlab('')+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        strip.background =element_rect(fill="white"))

ggsave('../Figures/VarImpPlotsall.png', width=12, height=10, dpi=500)
ggsave('../Figures/VarImpPlotsall.pdf', width=12, height=10)

```

# Session Info

```{r}
sessionInfo()
```