---
title: "Trait Specialisation Analyses"
author: "J C D Terry & S Gripenberg"
date: "17/01/2019"
output: 
  html_document: 
    toc: yes
---
# Packages and Data

```{r, message=FALSE, warning=FALSE}
rm(list=ls())

require(tidyverse)
require(bipartite)
require(corrplot)
require(knitr)
require(broom)
require(RColorBrewer)
require(caret)
require(cowplot)
require(pdp)
require(gridExtra)
require(phytools)
require(ggtree)                  
require(treeio)   

### To install ggtree from bioconductor:
# BiocManager::install('ggtree')

select<- dplyr::select # to ensure dplyr version of select is default

## Function to order bipartite network to minimise overlap
# source('OneSidedCCA.R')
```

```{r}
FW<-read_csv('../Data/FW.csv')
Trait<- read_csv('../Data/TidyTrait.csv')
InsectData <- read_csv("../Data/Insect data.csv")## Data set of all observed interactions
PhyloExtraSpec<-read.tree('../Data/PhyloExtraSpec.tree')

Trait%>%
  select(Codigo, TotUnits_collected,Codigo, Plant_species19,
         Plant_Family =Family)-> PlantTraitsToAdd


InsectData%>%
  left_join(PlantTraitsToAdd, by = 'Codigo')-> InsectData

```

# Size and Completentess of Data

```{r}
vegan::estimateR(InsectData$TOTAL)

rarecurve(t(InsectData$TOTAL), ylab = 'Interaction Count')

Fs<-table(InsectData$TOTAL)

## Manually calculating Chao1 Index:

f1=Fs[1] 
f2=Fs[2] 
n=sum(Fs)

## Sample coverage:
1 - (f1/n) * (  ((n-1)*f1)/((n-1)*f1 + 2*f2))

nrow(InsectData)

InsectData%>%
  summarise( 'Number of Insect species'= n_distinct(InsectSpCode ),
             'Number of Plant species'=n_distinct(Codigo ),
             'Total Insect COunt'=sum(TOTAL))%>%
  kable

InsectData%>%
  group_by(Order) %>%  summarise( 'Number of species'= n_distinct(InsectSpCode ),
                                  'Count' = sum(TOTAL))%>%
  kable

InsectData%>%
  filter(IncludeInFoodWeb=='Yes')%>%
  summarise( 'Insect species'= n_distinct(InsectSpCode ),
             'Plant species'=n_distinct(Codigo ),
             'Total Insect Count'=sum(TOTAL))%>%
  kable

InsectData%>%
  filter(IncludeInFoodWeb=='Yes')%>%
  nrow

Trait%>%
  filter(TotUnits_collected>200)%>%
  summarise('Percentage WellSampled Not Attacked'=mean(1-SeedPred_pres)*100)%>%
  kable

```

```{r}
Trait %>%
  filter(TotUnits_collected >200)%>%
  count(SeedPred_pres)

```

# Specialisation Statistics

##  Host specificity of internally feeding seed predators and whether seed predator taxa vary in their patterns of host use

### Basic Stats

```{r}
InsectData%>%
  group_by(Codigo)%>%
  summarise('N_Pred' = n_distinct(InsectSpCode))-> VulnRange

mean(VulnRange$N_Pred)
median(VulnRange$N_Pred)

VulnRange%>%
  count(N_Pred)%>%
  kable



InsectData%>%
  filter(TotUnits_collected>200)%>%
  group_by(Codigo)%>%
  summarise('N_Pred' = n_distinct(InsectSpCode))-> VulnRangeWS

mean(VulnRangeWS$N_Pred)
median(VulnRangeWS$N_Pred)

VulnRangeWS%>%
  count(N_Pred)%>%
  kable

```

### Diet Richness

N B. Using full dataset with the hymenoptera links in.

```{r}
InsectData %>%
  select(InsectSpCode, Order) %>%
  distinct(InsectSpCode, .keep_all = TRUE) -> Codes_Orders

InsectData  %>%
  group_by(InsectSpCode) %>%
  summarise('DietRichness' = n_distinct(Codigo), 
            'TotalInsects' = sum(TOTAL)) %>%
  mutate(InsectSampleSize = ifelse(TotalInsects==1, '1',
                                   ifelse(TotalInsects <10, '2-9' ,
                                          '\u2265 10'))) %>%
  left_join(Codes_Orders, by = "InsectSpCode")%>%
  mutate(InsectSampleSize = factor(InsectSampleSize, levels=c("1","2-9", "\u2265 10")))-> DataForFig5 


PlotSettingsFig5 <-  theme(panel.grid.major = element_blank(),
                           panel.grid.minor = element_blank(),
                           panel.background = element_blank(),
                           axis.line = element_line(colour = "black"))

DataForFig5 %>%
  filter(Order=='Coleoptera')%>%
  ggplot(aes(DietRichness, fill=InsectSampleSize))+geom_bar()+ 
  xlab('Diet Richness') +  ylab('Number of Insect Species')+
  scale_x_continuous(breaks=c(1:6), labels=1:6)+
  scale_fill_manual(values = c('grey90', 'grey50', 'grey20'),
                    name='Sample Size\nof Insects')+
  PlotSettingsFig5->Fig5i

DataForFig5 %>%
  filter(Order=='Lepidoptera')%>%
  ggplot(aes(DietRichness, fill=InsectSampleSize))+geom_bar()+ 
  xlab('Diet Richness') +  ylab('Number of Insect Species')+
  scale_x_continuous(breaks=c(1:6), labels=1:6)+
  scale_fill_manual(values = c('grey90', 'grey50', 'grey20'),
                    name='Sample Size\nof Insects')+
  PlotSettingsFig5->Fig5ii

DataForFig5 %>%
  filter(Order=='Hymenoptera')%>%
  ggplot(aes(DietRichness, fill=InsectSampleSize))+geom_bar()+ 
  xlab('Diet Richness') +  ylab('Number of Insect Species')+
  scale_x_continuous(breaks=c(1:6), labels=1:6, limits = c(0,6))+
  scale_fill_manual(values = c('grey90', 'grey50', 'grey20'),
                    name='Insect\nSample Size', 
                    labels=c("Singleton","<10", "\u2265 10"))+ 
  PlotSettingsFig5->Fig5iii

Figure5b<- plot_grid(Fig5i+theme(legend.position="none"),
                     Fig5ii+theme(legend.position="none"), 
                     Fig5iii+theme(legend.position="none"),
                     get_legend(Fig5iii), 
                     labels = c('i) Coleoptera',
                                'ii) Lepidoptera',
                                'iii) Hymenoptera'),
                     nrow = 1, rel_widths = c(3,3,3,1), scale = 0.9)

InsectData  %>%
  group_by(InsectSpCode) %>%
  summarise('DietRichness' = n_distinct(Codigo), 
            'TotalInsects' = sum(TOTAL)) %>%
  mutate(InsectSampleSize = ifelse(TotalInsects==1, 'Singleton',
                                   ifelse(TotalInsects <10, '<10' ,
                                          '>10'))) %>%
  left_join(Codes_Orders, by = "InsectSpCode")%>%
  mutate(InsectSampleSize = factor(InsectSampleSize, levels=c("Singleton","<10", ">10"))) %>%
  group_by(Order, InsectSampleSize)%>%
  mutate(Specialist = DietRichness ==1)%>%
  summarise(Specialists_n = sum(Specialist), Out_of = n_distinct(InsectSpCode))%>%
  kable


M<- as.table(rbind(c(63,7,15),c(95-63,10-7,30-15)))
dimnames(M) <- list(Generality = c("Specialist", 'NonSpecialist'),
                    Order = c("Coleoptera","Hymenoptera", "Lepidoptera"))
chisq.test(M) 
chisq.test(M)$expected  
chisq.test(M)$observed  

InsectData  %>%
  group_by(InsectSpCode) %>%
  summarise('DietRichness' = n_distinct(Codigo), 
            'TotalInsects' = sum(TOTAL)) %>%
  left_join(Codes_Orders, by = "InsectSpCode")%>%
  filter(TotalInsects>=10)%>%
  mutate(Specialist = DietRichness==1)-> DataForTest

summary(lm(data=DataForTest, Specialist~Order))


```

## What Fraction of Shared Plants Species in same family and same genera?

```{r}

InsectData %>%
  group_by(InsectSpCode)%>%
  summarise(NonSpecialist = n_distinct(Codigo)>1)%>%
  filter(NonSpecialist)-> NonSpecialists


InsectData %>%
  right_join(NonSpecialists, by = "InsectSpCode") %>%
  separate(Plant_species19, into=c('Plant_Genus', 'Plant_Specific'))%>%
  group_by(InsectSpCode)%>%
  summarise(Num_Families = n_distinct(Plant_Family), 
            Num_Genera   = n_distinct(Plant_Genus)) -> DiversityPrey

DiversityPrey$Num_Families %>% table # 
DiversityPrey$Num_Genera %>% table #  
```
### Repeat Without Single Records of interactions


```{r}
InsectData %>%
  filter(TOTAL>1)%>%
  group_by(InsectSpCode)%>%
  summarise(NonSpecialist = n_distinct(Codigo)>1)%>%
  filter(NonSpecialist) -> NonSpecialists_NoSingletons

InsectData %>%
  filter(TOTAL>1)%>%
  right_join(NonSpecialists_NoSingletons, by = "InsectSpCode") %>%
  separate(Plant_species19, into=c('Plant_Genus', 'Plant_Specific'))%>%
  group_by(InsectSpCode)%>%
  summarise(Num_Families = n_distinct(Plant_Family), 
            Num_Genera   = n_distinct(Plant_Genus)) -> DiversityPrey_NoSingletons

DiversityPrey_NoSingletons$Num_Families %>% table # 
DiversityPrey_NoSingletons$Num_Genera %>% table # 

```

### Plots of Vulnerability of Plant Species

```{r}


InsectData %>%
  group_by(Codigo)%>%
  filter(!is.na(TotUnits_collected))%>%
  summarise(Vuln=n_distinct(InsectSpCode),
            WellSampled= max(TotUnits_collected)>200)%>%   # Need to pick a number of the frame, all identical
  ggplot(aes(factor(Vuln), fill=WellSampled))+
  geom_histogram(stat='count')+
  ggtitle('')+
  xlab("Observed Number of Seed Predator Species")+
  ylab('Number of Plant Species')+
  scale_fill_manual(values = c('grey80', 'grey30'),
                    name='Seed Unit\nSample Size',
                    labels=c('< 200',
                             '\u2265 200'))+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black")) -> Figure1
Figure1


ggsave('../Figures/Figure1.png', Figure1, width=5, height=5, dpi=500 )
ggsave('../Figures/Figure1.pdf', Figure1, width=5, height=5)


InsectData %>%
  group_by(Codigo)%>%
  summarise(Vuln=n_distinct(InsectSpCode),
            WellSampled= max(TotUnits_collected)>200, 
            Name = max(Plant_species19))%>%
  arrange(desc(Vuln))%>% 
  head()%>%
  kable()

```


### Top-15 most generalist Insects
```{r}
InsectData %>%
  group_by(InsectSpCode)%>%
  summarise(Generality=n_distinct(Codigo),
            Name = max(FullSpeciesNameValid),
            Family  = max(Family ))%>%
  arrange(desc(Generality))%>%
  head(15)
```

# Insect Specialisation rates

```{r}

InsectData %>%
  group_by(InsectSpCode)%>%
  summarise(Generality=n_distinct(Codigo),
            Name = max(FullSpeciesNameValid),
            Family  = max(Family ))%>%
  count(Generality)%>% kable


InsectData %>%
  group_by(InsectSpCode)%>%
  summarise(InsectSampleSize = sum(TOTAL),
            Generality=n_distinct(Codigo),
            Name = max(FullSpeciesNameValid),
            Family  = max(Family ))%>%
  filter(InsectSampleSize>9)%>%
  count(Generality)%>% kable



InsectData %>%filter(InsectSpCode == 296)%>%
  select(FullSpeciesNameValid, Codigo, TOTAL)%>%
  kable

```


```{r}
InsectData %>%
  group_by(InsectSpCode)%>%
  summarise(InsectSampleSize = sum(TOTAL),
            Generality=n_distinct(Codigo),
            Name = max(FullSpeciesNameValid),
            Order  = max(Order ))%>%
  filter(InsectSampleSize>9)%>%
  group_by(Order)%>%
  count(Generality)%>% kable


```




# Specialisation in BCI Food Web

## Using Full FW (including single records)

```{r}
FW$Site <- 'BCI'
VARNAMES = c('Codigo','FullSpeciesNameValid', 'Site', 'KilledPerM2')


FW%>%
  group_by(InsectSpCode)%>%
  summarise(InsectSampleSize = sum(TOTAL),
            FullSpeciesNameValid = max(FullSpeciesNameValid),
            Family = max(Family), 
            Order = max(Order))-> InsectTaxaSampleSize
FW%>%
  left_join(select(InsectTaxaSampleSize, InsectSpCode, InsectSampleSize),
            by= 'InsectSpCode') -> FW

FW <- as.data.frame(FW)
NoSingFw<- as.data.frame(filter(FW, TOTAL >1 ))
WellSaFw<- as.data.frame(filter(FW, InsectSampleSize>=10))
WellSaFwNoSing<- as.data.frame(filter(FW, InsectSampleSize>=10,TOTAL >1 ))


IntMatrix_all<- frame2webs(FW,        varnames= VARNAMES)$BCI
IntMatrix_NoS<- frame2webs(NoSingFw , varnames= VARNAMES)$BCI
IntMatrix_ten<- frame2webs(WellSaFw , varnames= VARNAMES)$BCI
IntMatrix_tenNoS<- frame2webs(WellSaFwNoSing , varnames= VARNAMES)$BCI

```

# H2 Values of Combined Wb and Subwebs

```{r}
FW %>%
  filter(Order == 'Coleoptera' ) -> COL_Web
FW %>%
  filter(Order == 'Lepidoptera' ) -> LEP_Web

IntMatrix_Coleo<- frame2webs(COL_Web, varnames= VARNAMES)$BCI
IntMatrix_Lepid<- frame2webs(LEP_Web, varnames= VARNAMES)$BCI


data.frame('Web' = c('All', 'No Singletons', 'At least 10 Samples', '10 Samples and No Singles',
                     'Coleoptera', 'Lepidoptera'),
           'H2'=c(H2fun(IntMatrix_all, H2_integer = FALSE)[1] ,
                  H2fun(IntMatrix_NoS, H2_integer = FALSE)[1] ,
                  H2fun(IntMatrix_ten, H2_integer = FALSE)[1] ,
                  H2fun(IntMatrix_tenNoS, H2_integer = FALSE)[1] ,
                  H2fun(IntMatrix_Coleo, H2_integer = FALSE)[1] ,
                  H2fun(IntMatrix_Lepid, H2_integer = FALSE)[1] ))%>%
  kable
```


#Are Coleoptera or Lepidoptera more specialised?


```{r}
# standardised specialisation index d'
data.frame('d'=  dfun(t(IntMatrix_all))$dprime)%>%
  rownames_to_column(var = 'FullSpeciesNameValid')%>%
  left_join(InsectTaxaSampleSize, by='FullSpeciesNameValid' )-> DsAll

range(filter(DsAll, d>0)$d)


DsAll%>%
  arrange(d)%>%head(10) %>% kable

data.frame('d'=  dfun(t(IntMatrix_NoS))$dprime )%>%
  rownames_to_column(var = 'FullSpeciesNameValid')%>%
  left_join(InsectTaxaSampleSize, by='FullSpeciesNameValid' )-> DsNoS

range(filter(DsNoS, d>0)$d)


data.frame( 'd'= dfun(t(IntMatrix_ten))$dprime )%>%
  rownames_to_column(var = 'FullSpeciesNameValid')%>%
  left_join(InsectTaxaSampleSize, by='FullSpeciesNameValid' )-> Dsten

data.frame( 'd'= dfun(t(IntMatrix_tenNoS))$dprime )%>%
  rownames_to_column(var = 'FullSpeciesNameValid')%>%
  left_join(InsectTaxaSampleSize, by='FullSpeciesNameValid' )-> DstenNoS




data.frame('Web' = c('All', 'No Singletons', 'At least 10 Samples', '10 Samples and No Singles'),
           'd_median'=c(median(DsAll$d), median(DsNoS$d), median(Dsten$d), median(DstenNoS$d)),
           'd_max'=c(max(DsAll$d), max(DsNoS$d), max(Dsten$d), max(DstenNoS$d)),
           'd_min'=c(min(DsAll$d), min(DsNoS$d), min(Dsten$d), min(DstenNoS$d)))%>%
  kable

range(filter(Dsten, d>0)$d)

Dsten%>%
  arrange(d)%>%head %>% kable
```

## Order Level Specialisation

## Statistical Test


```{r}
wilcox.test(d~Order, data = DsAll) 
boxplot(d~Order, data = DsAll) 

wilcox.test(d~Order, data = Dsten) 
boxplot(d~Order, data = Dsten) 
```

## Specialisation Plots


```{r}
DsAll %>%
  mutate(TenOrMore = InsectSampleSize>=10)%>%
  filter(Order== 'Coleoptera')%>%
  ggplot(aes(x= d, fill=TenOrMore))+
  geom_histogram(position = 'stack', bins = 10)+
  ggtitle('')+
  xlab("Specialisation, d'")+
  ylab('Number of Insect Species')+
  #   scale_y_continuous(limits=c(0,80))+
  scale_fill_manual(values = c('grey80', 'grey30'),
                    name='Insect\nSample Size',
                    labels=c('< 10',
                             '\u2265 10'))+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"))-> Fig5ai


DsAll %>%
  mutate(TenOrMore = InsectSampleSize>=10)%>%
  filter(Order== 'Lepidoptera')%>%
  ggplot(aes(x= d, fill=TenOrMore))+
  geom_histogram(position = 'stack', bins = 10)+
  ggtitle('')+
  xlab("Specialisation, d'")+
  ylab('Number of Insect Species')+
  #scale_y_continuous(limits=c(0,80))+
  scale_fill_manual(values = c('grey80', 'grey30'),
                    name='Insect\nSample Size',
                    labels=c('< 10',
                             '\u2265 10'))+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black")) -> Fig5aii


Fig5a<-plot_grid(Fig5ai+theme(legend.position="none"),
                 Fig5aii+theme(legend.position="none"),
                 get_legend(Fig5aii), 
                 labels = c('i) Coleoptera',
                            'ii) Lepidoptera'),
                 nrow = 1, rel_widths = c(3,3,1), scale = 0.9)


DsAll %>%
  ggplot(aes(Order,d))+
  geom_boxplot()+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"))+
  ylab('Specialisation, d')+
  xlab('')


```


```{r}

Fig5<-plot_grid(Fig5a,Figure5b, ncol=1, labels = c('a)', 'b)'))
Fig5
ggsave('../Figures/Figure5.png',Fig5, width=12, height=8, dpi=500)
ggsave('../Figures/Figure5.pdf',Fig5, width=12, height=12)


```


# Whether phylogenetic relatedness link plant species that share seed predators.

## PAC

### Data Wrangling:

```{r, message=FALSE}
VARNAMES = c('Plant_species19','InsectSpCode', 'Site', 'KilledPerM2')

FW%>%
  left_join(PlantTraitsToAdd, by='Codigo')%>%
  mutate(Site = 'BCI')%>%
  separate(Plant_species19, into=c('Plant_Genus', 'Plant_Specific'), remove = FALSE, extra = 'drop')%>%
  as.data.frame-> PAC_data

PAC_data%>%
  filter(!Plant_species19%in% PhyloExtraSpec$tip.label)
# At the moment only seem to lose onw species 'Trichospermum_galeottii'

PAC_data%>%
  filter(Plant_species19%in% PhyloExtraSpec$tip.label) -> PAC_data
```

### PAC and Phylogenetic distance matrix

```{r}
PresentPACmatrix<-PAC(frame2webs(PAC_data,  varnames=VARNAMES)$BCI)
diag(PresentPACmatrix)<-NA

PhyloExtraSpec$tip.label %in% PAC_data$Plant_species19-> PhylInFW # Is the Species in food web?

```

```{r}
Pord<- order(PhyloExtraSpec$tip.label[PhylInFW]) # Getting order to match
PhyloDistsMatrix_all<- cophenetic.phylo(PhyloExtraSpec)
P1<-PhyloDistsMatrix_all[PhylInFW,PhylInFW]
PhyloDistsMatrix<- P1[Pord, Pord]

```

### How many potential inter-specific interactions


```{r}
sum(PresentPACmatrix>0.1, na.rm=TRUE)
sum(PresentPACmatrix>0.01, na.rm=TRUE)
nrow(PresentPACmatrix)

```

### Matrix specifying Same family or genus?

```{r}
PAC_data%>%
  arrange(Plant_species19) %>%
  distinct(Plant_species19, .keep_all = TRUE) %>%
  select(Plant_species19, Plant_Genus ,Plant_Family) -> PlantFamGen


L <- nrow(PlantFamGen)

ByRow <- matrix(PlantFamGen$Plant_Family,nrow = L, ncol=L, byrow =TRUE)
ByCol <- matrix(PlantFamGen$Plant_Family,nrow = L, ncol=L)
FamilyMatch<-  (ByRow==ByCol) & !is.na(PlantFamGen$Plant_Family)

ByRow <- matrix(PlantFamGen$Plant_Genus, nrow = L, ncol=L, byrow =TRUE )
ByCol <- matrix(PlantFamGen$Plant_Genus,nrow = L, ncol=L)
GenusMatch<- (ByRow==ByCol)
GenusMatch[is.na(GenusMatch)] <- FALSE## Deal with genus - NA matching:

diag(GenusMatch)<- NA
diag(FamilyMatch) <- NA
```


### Combining the matrices into a long form dataframe
```{r}
PhyloPAC = data.frame('PAC'= as.vector(PresentPACmatrix),
                      'PhyloDist' = as.vector(PhyloDistsMatrix),
                      'SameGenus' = as.vector(GenusMatch),
                      'SameFamily'= as.vector(FamilyMatch))

```

### Can any of these values predict PAC?

```{r}

PhyloPAC %>%
  filter(!is.na(PAC)) %>%
  filter(PAC!=0)%>%
  # filter(PhyloDist<180)%>%
  mutate(TaxonomicDistance = ifelse(SameGenus, 'Same Genus',
                                    ifelse(SameFamily, 'Same Family', 'Different Family')))%>%
  ggplot()+
  geom_point(aes(PhyloDist, PAC, col=TaxonomicDistance))+
  scale_color_grey(name='Taxonomic\nDistance')+
  geom_smooth(aes(PhyloDist, PAC), se=FALSE, col='red', method='lm')+
  # geom_smooth(aes(PhyloDist, PAC), se=FALSE, col='red', method='glm',method.args = list(family='binomial'))+
  xlab('Phylogenetic Distance')+
  ggtitle('')


ggsave('../Figures/FigureS6.png', width = 8, height=6,dpi = 600 )
ggsave('../Figures/FigureS6.pdf', width = 8, height=6)


```

### Mantel test

Comparing phylogenetic distance and PAC

```{r}
mantel(PresentPACmatrix, PhyloDistsMatrix) # Redo without 0 values??
```

### Just over 0 PACers

```{r}


#Linearise 

PACvalues <- as.vector(PresentPACmatrix)
Phylodistances <- as.vector(PhyloDistsMatrix)

Keepers<-PACvalues >0 & !is.na(PACvalues)
sum(Keepers)

plot(PACvalues[Keepers]~Phylodistances[Keepers])
plot(rank(PACvalues[Keepers])~rank(Phylodistances[Keepers]))

abline(lm(rank(PACvalues[Keepers])~rank(Phylodistances[Keepers])))

data.frame(PAC_Rank=rank(PACvalues[Keepers]),
           PhyloDist_Rank = rank(Phylodistances[Keepers])) %>%
  ggplot(aes(PAC_Rank, PhyloDist_Rank))+
  geom_point( alpha=0.5)+
  geom_smooth(method ='lm', se=FALSE, col='red')

data.frame(PAC_Rank=PACvalues[Keepers],
           PhyloDist_Rank = Phylodistances[Keepers]) %>%
  ggplot(aes(PAC_Rank, PhyloDist_Rank))+
  geom_point( alpha=0.5)+
  geom_smooth(method ='lm', se=FALSE, col='red')


cor.test(PACvalues[Keepers], Phylodistances[Keepers], method = 'spearman')


### Mantel test: doesn't work as is as too many blanks

No0_PresentPACmatrix<- PresentPACmatrix
No0_PhyloDistsMatrix<- PhyloDistsMatrix


No0_PresentPACmatrix[PresentPACmatrix==0]<-  NA
No0_PhyloDistsMatrix[PresentPACmatrix==0]<-  NA

#mantel(No0_PresentPACmatrix, No0_PhyloDistsMatrix, na.rm = TRUE) 


```


### Linear Models

Results are significant, but effect sizes / variation explained is tiny. Not a valid test as relationships are not independent. 

```{r}

LM_List<-bind_rows(
  tidy(lm(data = PhyloPAC, PAC ~ PhyloDist) ),
  tidy(lm(data = PhyloPAC, PAC ~ SameFamily)),
  tidy(lm(data = PhyloPAC, PAC ~ SameGenus) ))

LM_List %>%
  filter(term != '(Intercept)') %>%
  mutate(Significant = p.value < 0.05 ) %>%
  select(term, estimate, p.value, Significant)

```



# Plotting the Food web

```{r}
## Order by taxonomy
PhyloExtraSpec %>% 
  reorder.phylo(order = 'cladewise') -> x

x$tip.label %>%
  tbl_df() %>%
  dplyr::rename(Plant_species19 = value) -> PhylogenySpecies

PhylogenySpecies$TaxoOrder<- 1:nrow(PhylogenySpecies)


FW%>%
  left_join(PlantTraitsToAdd, by = 'Codigo')%>%
  left_join(PhylogenySpecies, by = 'Plant_species19')-> FW

```


### Dealing with missing species
```{r}
FW%>%filter(is.na(TaxoOrder))

'Trichospermum'     %in% PlantFamGen$Plant_Genus
'Malvaceae' %in% PlantFamGen$Plant_Family

# Find a slot for TRI6 
TRI6_order <- max(filter(FW, Plant_Family == 'Malvaceae')$TaxoOrder, na.rm = TRUE ) + 0.5

FW%>%
  mutate( TaxoOrder = ifelse(Codigo =='TRI6',
                             TRI6_order,
                             TaxoOrder  )) -> FW
```

Tidying up plant names (insect names just remove genus and unknown)

```{r}



## Making Names nicer:

InsectNameCleaner<-   function(str){
  
  ## Tidying up Insect names 
  str<- str_replace(str,pattern = 'genus ', replacement = '' )
  str<- str_replace(str,pattern = 'unknown ', replacement = '' )
  
  # Removing duplication
  Parts<- str_split(str, ' ') 
  
  New<-paste(rev(unique(rev(Parts[[1]]))),
             collapse = ' ')
  
  # Removing 'nr./near/cf. xxxx' 
  Parts<- str_split(New, ' ')[[1]]
  
  if('nr.' %in%   Parts |'near' %in%   Parts | 'cf.' %in% Parts){
    Parts<- Parts[1:3]
  }
  return(paste(Parts, collapse = ' '))
}



FW %>%
  arrange(TaxoOrder)%>%
  separate(Plant_species19,
           into = c('PlantGenus', 'PlantSpecies'),
           remove = FALSE, fill = 'right', extra = 'drop')   %>%
  mutate(NicePlantName = paste(PlantGenus, PlantSpecies),
         Site='BCI')%>%
  rowwise()%>%
  mutate(Site= 'BCI',
         Insect  = InsectNameCleaner(FullSpeciesNameValid)) %>%
  as.data.frame-> ForPlot

IntMatrix<- frame2webs(ForPlot, varnames=c('NicePlantName','Insect', 'Site', 'KilledPerM2'))

```

## Network Ordered by compartment size (effectively specialisation)

```{r}

Ordering<-  bipartiteD3::OrderByCrossover(IntMatrix$BCI)

TaxoOrderWebSort <- IntMatrix$BCI[rev(Ordering$PrimaryOrder), rev(Ordering$SecondaryOrder)]

png('../Figures/Figure4.png', units = 'in',width = 15, height = 10, res = 1000)
par(mai=c(8,0,2,0), oma=c(3,0,3,0), xpd=TRUE)
plotweb(TaxoOrderWebSort,method = 'normal', text.rot = 90, labsize = 0.5, ybig = 2.5)
dev.off()

pdf('../Figures/Figure4.pdf', width = 15, height = 10 )
par(mai=c(8,0,2,0), oma=c(3,0,3,0), xpd=TRUE)
plotweb(TaxoOrderWebSort,method = 'normal', text.rot = 90, labsize = 0.5, ybig = 2.5)
dev.off()

```

##Split Plot by Insect Group

```{r}
SplitMatrices<- frame2webs(ForPlot, varnames=c('NicePlantName','Insect', 'Order', 'KilledPerM2'))

pdf('../Figures/FigureS4.pdf', width = 10, height = 10)
par(mfrow=c(2,1), mai=c(8,2,6,2), mar = c(2, 2,2, 2) + 0.1, xpd=TRUE)
for( SUBWEB_NAME in c('Coleoptera','Lepidoptera')){
  SUBWEB <- SplitMatrices[[SUBWEB_NAME]]
  Ordering<-  bipartiteD3::OrderByCrossover(SUBWEB)
  plotweb(SUBWEB[rev(Ordering$PrimaryOrder), rev(Ordering$SecondaryOrder)],
          method = 'normal', text.rot = 90, labsize = 0.5, ybig = 2.5)
  title(main = SUBWEB_NAME)
}
dev.off()


png('../Figures/FigureS4.png', width = 10, height = 6, units='in', res=1000)
par(mfrow=c(2,1), mai=c(8,2,6,2), mar = c(2, 2,2, 2) + 0.1, xpd=TRUE)
for( SUBWEB_NAME in c('Coleoptera','Lepidoptera')){
  SUBWEB <- SplitMatrices[[SUBWEB_NAME]]
  Ordering<-  bipartiteD3::OrderByCrossover(SUBWEB)
  plotweb(SUBWEB[rev(Ordering$PrimaryOrder), rev(Ordering$SecondaryOrder)],
          method = 'normal', text.rot = 90, labsize = 0.5, ybig = 2.5)
  title(main = SUBWEB_NAME)
}
dev.off()

```

## Food web without singleton observations

```{r}
ForPlot%>%
  filter(TOTAL >1) %>%
  frame2webs(varnames=c('NicePlantName','Insect',
                        'Site', 'KilledPerM2'))->NoSing_IntMatrix

Ordering<-  bipartiteD3::OrderByCrossover(NoSing_IntMatrix$BCI)

NoSing_TaxoOrderWebSort <- NoSing_IntMatrix$BCI[rev(Ordering$PrimaryOrder), rev(Ordering$SecondaryOrder)]

png('../Figures/FigureS5.png', units = 'in',width = 15, height = 10, res = 1000)
par(mai=c(8,0,2,0), oma=c(3,0,3,0), xpd=TRUE)
plotweb(NoSing_TaxoOrderWebSort,method = 'normal', text.rot = 90, labsize = 0.5, ybig = 2.5)
dev.off()

pdf('../Figures/FigureS5.pdf',width = 15, height = 10 )
par(mai=c(8,0,2,0), oma=c(3,0,3,0), xpd=TRUE)
plotweb(NoSing_TaxoOrderWebSort,method = 'normal', text.rot = 90, labsize = 0.5, ybig = 2.5)
dev.off()

```

# Plotting Phylogeny

```{r warning=FALSE}
PlotPhylo <- PhyloExtraSpec

data.frame(Plant_species19=PlotPhylo$tip.label)%>%
  left_join(Trait, by= 'Plant_species19') %>%
  select(Plant_species19,Family,TotUnits_collected, SeedPred_pres,
         Hymeno_pres, Lepid_pres , Coleo_pres) %>%
  mutate(PlantLabel= str_replace_all(Plant_species19, pattern = "_", " "),
         WellSampled= ifelse(TotUnits_collected<200 | is.na(TotUnits_collected),
                             'Under-Sampled','Well-Sampled'),
         Predated= ifelse(SeedPred_pres==0 | is.na(SeedPred_pres),
                          'Not-Predated', 'Predated'),
         ColourCode = paste(WellSampled,Predated) ,
         WaspPic = ifelse(Hymeno_pres, 'Wasp-silhouette.png', NA), 
         MothPic = ifelse(Lepid_pres, 'Moth.png', NA),
         BeetlePic = ifelse(Coleo_pres, 'Beetle.png', NA))%>%
  select(PlantLabel,WellSampled, Predated, ColourCode, WaspPic, MothPic, BeetlePic, TotUnits_collected) -> DF

PlotPhylo$tip.label<-str_replace_all(PlotPhylo$tip.label, pattern = "_", " ")

ToDrop <- DF$taxe[is.na(DF$TotUnits_collected)]
TrimmedTree <- drop.tip(PlotPhylo, tip = ToDrop)

WellSampledTree <- drop.tip(PlotPhylo, tip = DF$PlantLabel[DF$WellSampled =='Under-Sampled'])

ggtree(WellSampledTree, layout = 'circular', col='darkgrey') %<+% DF +
  scale_fill_manual(values = c( 'white' , 'Black' ),
                    labels= c('Not predated', 'Predated'),
                    name='')+
  theme(legend.position=c(0.1, 0.95), legend.background = element_blank())+
  geom_tippoint(aes(fill=Predated), shape=21)+
  # labs(caption='Phylogenetic distribution of observed predators amongst the "well-sampled" species')+
  geom_tiplab2(aes(image=WaspPic), geom='image', hjust = 0.1, offset=25, size=0.05 )+
  geom_tiplab2(aes(image=MothPic), geom='image', hjust = 0.1, offset=15, size=0.02)+
  geom_tiplab2(aes(image=BeetlePic), geom='image', hjust = 0.1, offset=5, size=0.02)

ggsave('../Figures/Figure2.png', width = 7, height = 7, dpi=900)
ggsave('../Figures/Figure2.pdf', width = 7, height = 7)



ggtree(TrimmedTree, layout = 'circular', branch.length = 'none', col='darkgrey') %<+% DF +
  scale_fill_manual(values = c( 'lightgrey' ,'darkgrey','white' , 'Black'),
                    labels= c('Not-Predated, Under-Sampled','Predated Under-Sampled',
                              'Not-Predated Well-Sampled','Predated Well-Sampled'),
                    name='')+
  geom_tippoint(aes(fill=ColourCode), shape=21, size=3) +
  theme(legend.position=c(0.1, 0.9), legend.background = element_blank())+
  geom_tiplab2(size=2, hjust = -0.1, fontface = "italic")+
  labs(caption='Cladogram of plant species detailing observed predators and sampling intensity')

ggsave('../Figures/FigureS2all.pdf', width = 15, height = 15)
ggsave('../Figures/FigureS2all.png', width = 15, height = 15, dpi = 600)



ggtree(WellSampledTree, layout = 'circular', col='darkgrey') %<+% DF +
  scale_fill_manual(values = c( 'white' , 'Black' ),
                    labels= c('Not predated', 'Predated'),
                    name='')+
  theme(legend.position=c(0.1, 0.9), legend.background = element_blank())+
  geom_tippoint(aes(fill=Predated), shape=21)+
  geom_tiplab2(size=2, hjust = -0.1, fontface = "italic")+
  labs(caption='Phylogenetic distribution of observed predators amongst the "well-sampled"" species')

ggsave('../Figures/FigureS2.pdf', width = 12, height = 12)
ggsave('../Figures/FigureS2.png', width = 12, height = 12, dpi = 600)
```

# Session Info

```{r}
sessionInfo()

```



